\part{Introduction}
\section{Foreword}
For the course 'kursusnavn' have it been required to conduct an investigation for a certain subject and then reflect over this subject. We have choosen to focus our attention on estimation techniques for development in software projects. Based on readings (kilde?) and own experience, we think that this subject have been a hard thing to do in and have often been a  troublesome task to perform. Because of this, we have chosen to base our investigation on estimates and more precisely estimation techniques given from the course book 'kilde'. 

\section{Background}
For this project we have to aim our investigation towards a certain project, to get some sensible data to analyse and reflect upon. We have chosen to use our second year project in the course 'Second Year Project: Software Development in Large Teams with International Collaboration'. In short, this project consists of a collaboration with a university group for a Singaporean university, where we been given the task to develop a server and a client for some kind of media service. The server will expose services which the international group will use to develop a client, which uses these services. We to, will have to make a client, which uses our servers services, but the collaboration and the serves services is the main objective of the project and there most of our attention will be. This project will start in February and go to the end of May, where the server and client code and a associated report of 20-30 pages will have to be handed in. To help manage the project and reach our project deadline we will be using SCRUM (kilde til beskrivelse af scrum?) development method. This will enable us to apply different estimation techniques to the sprints, during the project period, which in the end will the techniques presented in this report. The team consists of 5 members with prior relationship to each other and with equal software developing experience in the required programming language C# (kilde til C#?). 
SCRUM
Team size, length of project, project size(Scope, complexity, target)

\section{Problem definition}
For a software project, where the team will consist of 5 people, how does a certain estimation technique impact the outcome of the project regarding to quality of the software as well as how the final deadline were handled. 
\begin{itemize}
\item What prerequisites are necessary in order to perform accurate estimates of the workload in a software project?
\item How do different estimation techniques affect the teams' ability to meet project deadlines?
\item How does the working conditions influence the precision and usefulness of the various estimation techniques?	
\item Is one estimation technique more appropriate than others in a project of size and scope similar to a 4 month university project?


\item What kind of estimation techniques is 'optimal' to use for a software project and how can these be incorporated in some of the earlier phases of the development
\item How does the techniques different from each other and what are the pros and cons for the various techniques
\item How can a team benefit by using a certain estimating technique
\item What and why does the change of success for a software project depend so deeply upon the estimation of the tasks?
\item 

\end{itemize}
\section{Motivation}
In the start of every software project, the first things that stakeholders, executive people and other similar persons are interested in, is the price of the project and the time frame that he project is about to enter. Questions like: "When can we expect the first prototype" and "When is the product ready to be shipped of to customers", are ones that often is needed to be answered in the start of a project typical by a manager. For the managers point of view, this can often be a challenge to answer, mainly due to the fact the 'requirements' for the project, at this point, are often vaguely defined and more a wish-list than actually requirements, that can be translated into program features. This combined with the fact, that developing a pierce of software from scratch often require a certain amount of innovation. Even though the project  will use known and common technologies and developing methods, these can be combined in a new way and this can both be time consuming and some time troublesome. \\
Because of this, many estimates for software project have been poorly and predicted delivery dates have often been exceeded with several percentages (KILDE OOA/D bogen). This could point towards that estimating projects should be handled by specialist which would have an objective view of the project, like its seen in civil engineering. Here an estimator does nothing else than trying to accurate estimate the tasks of the project. This means that estimates of civil engineering often are more precise than estimates in software projects. This is due to the fact, that in civil engineering when starting a project, its for the most time possible to use experience from earlier similar projects, which make the estimates more precise. \\
Clearly estimating in software projects is milestones behind civil engineering, where estimation specialist have a big importance among other things. Therefore a lot of research is done in the field of software engineering and many optimistic attempts have been made to develop estimating techniques, that tries to limit the chance of estimations of tasks is so off, that it will impact the whole project and especially the final delivery date. 
Therefore we will, in the following sections, describe, discuss and analyse various estimating techniques and test some of them in a real software project. Many techniques have been developed and some have archived more success than others, but it is clear that we have to limit our scope and focus on only a couple of techniques. Because of this, the following sections will address and describe the following techniques: Delphi, planning poker, PERT and .... . \\
We have choosen to limit our focus to these three, because of the prerequisites that is needed to use these techniques, among other things. Other techniques like 'CoComo' and 'function point analysis' requires things like experience from earlier similar projects, which the team does not have. The three techniques we will direct our attention towards, is not however the 'right' techniques or the ones that deliver the best results. These three techniques share the same chance of errors and fault with all other techniques. We have simply to focus on these, because we believe that this is the techniques that fits our project scope, size and complexity the best. 
